\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontawesome5}
\input{glyphtounicode}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.58in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.15in}
\addtolength{\topmargin}{-.78in}
\addtolength{\textheight}{1.28in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

\begin{center}
  {\Huge \scshape Tejas S}\\[-2pt]
  {\small Bengaluru, India}\\[3pt]
  {\small
    \faPhone\ +91-8618904742 \quad
    \href{mailto:tejassureshofficial@gmail.com}{\faEnvelope\ \underline{tejassureshofficial@gmail.com}} \quad
    \href{https://tejassureshofficial.in}{\faGlobe\ \underline{tejassureshofficial.in}} \quad
    \href{https://www.linkedin.com/in/tejas-s-57138816a/}{\faLinkedin\ \underline{LinkedIn}} \quad
    \href{https://github.com/Tez861910}{\faGithub\ \underline{GitHub}}
  }
\end{center}
\vspace{-8pt}

\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Full-stack product developer building software that has to hold up in real workflows, not just demos. Recent work spans web product platforms, content-rich company platforms, a Windows manufacturing app, and a Flutter + Rust utility suite. I work best where product clarity, interface structure, and implementation quality need to reinforce one another.}
\resumeSubHeadingListEnd
\vspace{-12pt}

\section{Core Capabilities}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Product engineering}{: workflow-oriented UI, dashboard systems, protected flows, content architecture} \\
    \textbf{Frontend \& product UI}{: React, Next.js, TypeScript, Vite, Tailwind CSS, Framer Motion, Material UI} \\
    \textbf{Backend \& APIs}{: Node.js, Express, Prisma, Sequelize, REST APIs, auth, validation, uploads} \\
    \textbf{Desktop \& cross-platform}{: .NET 8, WinUI 3, Win2D, AssimpNet, Flutter, Flutter Rust Bridge, multi-platform release} \\
    \textbf{Data \& delivery}{: PostgreSQL, MySQL, SQLite, Git, GitHub Actions, build and release workflow support}
  }}
\end{itemize}
\vspace{-14pt}

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Engineer --- Product, Web \& Desktop}{Dec 2024 -- Dec 2025}
    {Printalytix}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem{Worked across customer-facing and internal product surfaces, from upload-heavy web flows to operations-oriented tooling.}
      \resumeItem{Built and evolved \textbf{MIND} as a .NET 8 Windows desktop app for 3D model inspection, manufacturing guidance, screenshot capture, and report generation.}
      \resumeItem{Delivered React and Node-based systems with protected workflows, validation, uploads, and maintainable product structure.}
      \resumeItem{Contributed across frontend, backend, and workflow design instead of staying in a single layer of the stack.}
    \resumeItemListEnd

  \resumeSubheading
    {Volunteer --- Full-Stack Development}{Oct 2023 -- Jan 2024}
    {Old Dominion University}{Norfolk, VA, USA}
    \resumeItemListStart
      \resumeItem{Built a university threads platform with role-based access, discussion flows, and real-time messaging.}
      \resumeItem{Delivered an examination management system covering assessment workflows, submissions, and administrative coordination.}
      \resumeItem{Worked on backend queries, caching, and application structure to keep the platform responsive as features expanded.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Pettige} $|$ \emph{Flutter, Dart, Rust, SQLite, FFmpeg}}{}
    \resumeItemListStart
      \resumeItem{Privacy-first, cross-platform utility suite with \textbf{30+ tools} across PDF, image, audio, video, QR, OCR, encrypted storage, and developer workflows.}
      \resumeItem{Built it around dedicated PDF Studio, Image Studio, Audio Studio, Video Studio, and Dev Workbench flows so the product stays navigable as the tool surface grows.}
      \resumeItem{Designed a split architecture where Flutter handles routing and the product shell while Rust performs heavy local processing with native-style performance.}
      \resumeItem{Structured SQLite-backed storage around on-device persistence, resumable uploads, and AES-256-GCM file protection.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{Open Solar Toolkit} $|$ \emph{React 19, TypeScript, Tailwind, DnD Kit, Recharts}}{}
    \resumeItemListStart
      \resumeItem{Solar operations product covering \textbf{7 workstreams} across administration, project management, sales, supply chain, installation, maintenance, and reporting.}
      \resumeItem{Built the UI as a set of specialised operational surfaces instead of one generic admin panel.}
      \resumeItem{Treated it as a product workspace rather than a static frontend, with backend hooks, tests, linting, and structural validation in place.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{MIND Manufacturing Intelligence} $|$ \emph{.NET 8, C\#, WinUI 3, Win2D, AssimpNet}}{}
    \resumeItemListStart
      \resumeItem{Windows desktop workflow that brings model viewing, inspection, manufacturing guidance, screenshots, and reporting into one application.}
      \resumeItem{Worked across views, view models, rendering services, assets, and structured outputs rather than treating it as only a rendering demo.}
      \resumeItem{Shows range beyond web work into workflow-heavy internal software where operator clarity and correctness matter.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{ChemLife Innovations Platform} $|$ \emph{Next.js 14, React 18, TypeScript, Tailwind}}{}
    \resumeItemListStart
      \resumeItem{Content-rich company platform with reusable data models for technologies, concepts, awards, and knowledge content.}
      \resumeItem{Structured the site so technical credibility, educational content, and future lead-generation flows can live in one maintainable system.}
      \resumeItem{Balanced technical credibility, educational content, and business inquiry flow in the same product surface.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{Resolute Solutions Site} $|$ \emph{React 19, Vite, Tailwind, EmailJS, PWA}}{}
    \resumeItemListStart
      \resumeItem{Live multi-vertical business site covering \textbf{4 service lines} with routed inquiry flows and structured catalogue content.}
      \resumeItem{Carried the work through to production delivery instead of stopping at a local prototype.}
      \resumeItem{Demonstrates multi-theme component reuse and content structuring in a real client-facing setting.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{Printalytix Platform} $|$ \emph{React 19, Redux Toolkit, Node.js, Express, Prisma}}{}
    \resumeItemListStart
      \resumeItem{Full-stack workflow product for customer intake, uploads, protected operations, and ongoing internal follow-through.}
      \resumeItem{Worked across frontend, backend, and data layers so validation, access rules, and operational tooling behaved like one system.}
      \resumeItem{Helped modernise the frontend workflow while keeping richer form, table, and upload surfaces intact.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{University Threads Platform} $|$ \emph{React, Material UI, Express, Sequelize, MySQL}}{}
    \resumeItemListStart
      \resumeItem{Earlier multi-user collaboration system that still shows the foundations of my full-stack approach.}
      \resumeItem{Built around authentication, validation, rate limiting, logging, and role-aware behaviour instead of static page rendering alone.}
      \resumeItem{Useful as a portfolio piece because it demonstrates the shared-system thinking beneath later product work.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Computer Applications (BCA) --- Computer Science}{Aug 2018 -- Aug 2024}
    {Bengaluru North University}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem{Built a foundation in DBMS, web development, data structures, and algorithms.}
      \resumeItem{Completed a final-year project centred on full-stack web development with MySQL.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
