\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontawesome5}
\input{glyphtounicode}
\usepackage[sfdefault]{roboto}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.62in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.24in}
\addtolength{\topmargin}{-.92in}
\addtolength{\textheight}{1.82in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\begin{document}

\begin{center}
  {\Huge \scshape Tejas S}\\[-2pt]
  {\small Bengaluru, India}\\[3pt]
  {\small
    \faPhone\ +91-8618904742 \quad
    \href{mailto:tejassureshofficial@gmail.com}{\faEnvelope\ \underline{tejassureshofficial@gmail.com}} \quad
    \href{https://tejassureshofficial.in}{\faGlobe\ \underline{tejassureshofficial.in}} \quad
    \href{https://www.linkedin.com/in/tejas-s-57138816a/}{\faLinkedin\ \underline{LinkedIn}} \quad
    \href{https://github.com/Tez861910}{\faGithub\ \underline{GitHub}}
  }
\end{center}
\vspace{-8pt}

\section{Summary}
\resumeSubHeadingListStart
  \resumeItem{Full-stack product developer building workflow-heavy software across web, desktop, and cross-platform applications. Recent work spans React and Next.js product platforms, a .NET Windows app for 3D manufacturing workflows, and a Flutter + Rust utility suite. Strongest fit is product engineering where UX clarity, maintainable architecture, and real operational use all matter.}
\resumeSubHeadingListEnd
\vspace{-12pt}

\section{Core Stack}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Frontend}{: React, Next.js, TypeScript, Vite, Tailwind CSS, Framer Motion} \\
    \textbf{Backend \& APIs}{: Node.js, Express, Prisma, REST APIs, auth, validation, uploads} \\
    \textbf{Desktop \& 3D}{: .NET 8, WinUI 3, Win2D, AssimpNet, screenshot and document workflows} \\
    \textbf{Cross-platform, Data \& Delivery}{: Flutter, Flutter Rust Bridge, PostgreSQL, MySQL, SQLite, GitHub Actions, multi-platform release}
  }}
\end{itemize}
\vspace{-14pt}

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Software Engineer --- Product, Web \& Desktop}{Dec 2024 -- Dec 2025}
    {Printalytix}{Bengaluru, India}
    \resumeItemListStart
      \resumeItem{Built customer-facing and internal product surfaces across React and Node-based systems with upload-heavy flows, validation, and protected operations.}
      \resumeItem{Worked on \textbf{MIND}, a .NET 8 Windows desktop app for 3D model inspection, manufacturing guidance, screenshots, and report generation.}
      \resumeItem{Contributed across frontend, backend, and workflow design instead of staying in a single layer of the stack.}
    \resumeItemListEnd

  \resumeSubheading
    {Volunteer --- Full-Stack Development}{Oct 2023 -- Jan 2024}
    {Old Dominion University}{Norfolk, VA, USA}
    \resumeItemListStart
      \resumeItem{Built a university threads platform with role-based access, discussion flows, and real-time messaging.}
      \resumeItem{Delivered an examination management system covering assessment workflows, submissions, and administrative coordination.}
      \resumeItem{Worked on backend queries, caching, and application structure to keep the platform responsive as features expanded.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Pettige} $|$ \emph{Flutter, Rust, SQLite, FFmpeg}}{}
    \resumeItemListStart
      \resumeItem{Cross-platform local-first utility suite with \textbf{30+ tools} across PDF, image, audio, video, QR, OCR, encrypted storage, and developer workflows.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{Open Solar Toolkit} $|$ \emph{React 19, TypeScript, Tailwind, DnD Kit}}{}
    \resumeItemListStart
      \resumeItem{Role-based solar operations platform spanning \textbf{7 workstreams} across sales, planning, supply chain, installation, maintenance, and reporting.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{MIND Manufacturing Intelligence} $|$ \emph{.NET 8, WinUI 3, Win2D, AssimpNet}}{}
    \resumeItemListStart
      \resumeItem{Windows desktop workflow for 3D model analysis, manufacturing guidance, screenshots, and structured report generation.}
    \resumeItemListEnd
    \vspace{-10pt}

  \resumeProjectHeading
    {\textbf{ChemLife + Resolute} $|$ \emph{Next.js, React, Tailwind, EmailJS}}{}
    \resumeItemListStart
      \resumeItem{Company platforms with reusable content systems, routed inquiry flows, and multi-vertical presentation across biotech and B2B delivery.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8pt}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Computer Applications (BCA) --- Computer Science}{Aug 2018 -- Aug 2024}
    {Bengaluru North University}{Bengaluru, India}
\resumeSubHeadingListEnd

\end{document}
